\begin{thebibliography}{00}

\bibitem{microservices-general} P. Giessler, ``Dom\"anengetriebener Entwurf von ressourcenorientierten Microservices'', Karlsruher Institut für Technologie (KIT), 2018

\bibitem{spring-cloud} 
Spring Cloud \url{https://spring.io/projects/spring-cloud} (Last access: 2021/02/11, 11 am)

\bibitem{from-monolith} R. Chen, S. Li and Z. Li, "From Monolith to Microservices: A Dataflow-Driven Approach," 2017 24th Asia-Pacific Software Engineering Conference (APSEC), Nanjing, 2017, p. 473

\bibitem{sm1} W. Li, Y. Lemieux, J. Gao, Z. Zhao and Y. Han, "Service Mesh: Challenges, State of the Art, and Future Research Opportunities," 2019 IEEE International Conference on Service-Oriented System Engineering (SOSE), San Francisco East Bay, CA, USA, 2019, pp. 122-1225

\bibitem{sm2} Was ist ein Service Mesh? - \url{https://www.redhat.com/de/topics/microservices/what-is-a-service-mesh} (Last access: 2021/02/11, 12 am)

\bibitem{sm3} Indrasiri, Kasun., and Prabath. Siriwardena. ``Microservices for the Enterprise": Designing, Developing, and Deploying / by Kasun Indrasiri, Prabath Siriwardena. 1st ed. 2018., Apress, 2018

\bibitem{sm4}
K. Y. Ponomarev, ``Attribute-Based Access Control in Service Mesh," 2019 Dynamics of Systems, Mechanisms and Machines (Dynamics), Omsk, Russia, 2019, pp. 1-4

\bibitem{linkerd-github} linkerd/linkerd2 @ GitHub - \url{https://github.com/linkerd/linkerd2} (Last access: 2021/02/17, 11 am)

\bibitem{istio-github} istio/istio @ GitHub - \url{https://github.com/istio/istio} (Last access: 2021/02/17, 11 am)

\bibitem{istio-linkerd-compare-1} Kubernetes Service Mesh: A Comparison of Istio, Linkerd and Consul - \url{https://platform9.com/blog/kubernetes-service-mesh-a-comparison-of-istio-linkerd-and-consul/} (Last access: 2021/02/17, 11 am)

\bibitem{istio-linkerd-compare-2} Service Mesh: Einführung \& Vergleich von Istio und Linkerd - \url{https://www.predic8.de/service-mesh-microservices.htm}  (Last access: 2021/02/17, 11 am)

\bibitem{linkerd-circuit-breaker} Circuit breaker support? - \url{https://github.com/linkerd/linkerd2/issues/2846} (Last access: 2021/02/17, 2 pm)

\bibitem{fowler} Microservices - \url{https://martinfowler.com/articles/microservices.html} (Last access: 2021/02/17, 4 pm)

\bibitem{k8s} Konzepte | Kubernetes - \url{https://kubernetes.io/de/docs/concepts/} (Last access: 2021/02/18, 3 pm)

\bibitem{linkerd-docs-faq} Linkerd: FAQ - \url{https://linkerd.io/2/faq/} (Last access: 2021/02/18, 6 pm)

\bibitem{linkerd-docs-no-envoy} Why Linkerd doesn't use Envoy - \url{https://linkerd.io/2020/12/03/why-linkerd-doesnt-use-envoy/} (Last access: 2021/02/18, 6 pm)

\bibitem{linkerd-docs-arch} Linkerd: Architecture - \url{https://linkerd.io/2/reference/architecture/} (Last access: 2021/02/18, 6 pm)

\bibitem{linkerd-get-started} Linkerd: Get started - \url{https://linkerd.io/2/getting-started/} (Last access 2021/02/20, 3 pm)

\bibitem{istio-docs-arch} Istio: Architecture - \url{https://istio.io/latest/docs/ops/deployment/architecture/} (Last access: 2021/02/18, 6 pm)

\end{thebibliography}